---
output: html_document
editor_options: 
  chunk_output_type: console
format:
  html:
    html-table-processing: none
    toc-depth: 3
---

# Concordances {.unnumbered}

This appendix lists concordances between prior catalogues of Werner's works and WerW. For concordances of historic and modern inventories, see [Inventories](inventories.qmd).

```{r packages and functions}
#| include: false
library(tidyverse)
library(yaml)
library(gt)
source("script/utils.R")
options(readr.show_col_types = FALSE)

params <- read_yaml("data/config.yml")

print_concordance <- function(catalogue, notes = NULL) {
  if (!is.null(notes))
    notes <- read_csv(notes)
  else
    notes <- tibble(number = "__none__", notes = "")
  
  read_rds("data_generated/works.rds") %>% 
    left_join(
      read_csv("data/catalogue_overview.csv") %>% distinct(group, file),
      by = "group"
    ) %>% 
    unite(group:number, col = "id", sep = ".", na.rm = TRUE) %>%
    mutate(
      number = .data[[catalogue]],
      id = str_glue("[{id}](/groups/{file}.html#work-{id})")
    ) %>%
    separate_longer_delim(number, delim = ", ") %>% 
    select(number, id) %>% 
    mutate(number = str_remove(number, " \\(\\?\\)$")) %>% 
    bind_rows(notes) %>% 
    filter(!is.na(number), number != "__none__") %>%
    summarise(
      .by = number,
      id = str_flatten_comma(id, na.rm = TRUE),
      notes = str_flatten_comma(notes, na.rm = TRUE)
    ) %>%
    mutate(id = if_else(id == "", "–", id)) %>% 
    arrange(str_rank(number, numeric = TRUE)) %>% 
    gt() %>%
    cols_width(number ~ px(80), id ~ px(160)) %>%
    fmt_markdown(columns = id) %>% 
    cols_label(id = params$catalogue_prefix) %>% 
    sub_missing(columns = notes, missing_text = "") %>% 
    tab_options(
      column_labels.font.weight = "bold",
      table.align = "left",
      table_body.hlines.style = "none"
    )
}
```


## @Dopf1956 (Dopf)

```{r Dopf}
#| echo: false
#| output: asis
print_concordance("Dopf")
```


## @Harich1932 (HarBu)

```{r HarBu}
#| echo: false
#| output: asis
print_concordance("HarBu")
```


## @Harich1990 (HarCa)

The following table reproduces the table of contents of the unfinished catalogue of Werner's works by @Harich1990. Here, we refer to entries in this catalogue by work groups and the (probably final) work numbers, which appear in broad red ink in the top left corner of each card.

```{r HarCa overview}
#| echo: false
#| output: asis

read_csv("data/HarCa_groups.csv") %>% 
  fill(super_number, super_title) %>% 
  unite(super_number, super_title, col = "super", sep = ". ") %>% 
  gt(groupname_col = "super") %>%
  cols_label(number = "", sub = "") %>% 
  sub_missing(missing_text = "") %>%
  tab_style(
    style = list(
      cell_text(weight = "bold"),
      cell_borders("top", color = "#d3d3d3", weight = "2px")
    ),
    locations = cells_body(rows = 34)
  ) %>%
  tab_options(
    column_labels.font.weight = "bold",
    row_group.background.color = "grey90",
    table_body.hlines.style = "none"
  )
```

Generally, Hárich included works from the 1737/38 inventory as separate works in his catalogue, even if the work title is so generic that it may correspond to an extant work.

```{r HarCa entries}
#| echo: false
#| output: asis
print_concordance("HarCa", notes = "data/HarCa_notes.csv")
```


## @Petermayr2020 (PetSi)

```{r PetSi}
#| echo: false
#| output: asis
print_concordance("PetSi")
```


## @Petermayr2015 (PetWe)

```{r PetWe}
#| echo: false
#| output: asis
print_concordance("PetWe")
```


## @Reichert1935 (ReiMa)

```{r ReiMa}
#| echo: false
#| output: asis
print_concordance("ReiMa")
```


## @WinklerKlement2020 (WinMa)

```{r WinMa}
#| echo: false
#| output: asis
print_concordance("WinMa")
```
