---
output: html_document
editor_options: 
  chunk_output_type: console
format:
  html:
    html-table-processing: none
---

# Inventories {.unnumbered}

```{r packages}
#| include: false
library(tidyverse)
library(gt)
source("script/utils.R")
options(readr.show_col_types = FALSE)
```

## Eisenstadt

The inventory of Eisenstadt was finalized in 1837 [@EisenstadtInv1837]. The table of sources is written on the verso pages, which are numbered (with odd numbers!). For selected entries, the recto pages contain annotations indicating new parts that should be created (column “notes” in the table below). Groups have been numbered with uppercase letters. Thereby, the combination of group letter and inventory number corresponds to the modern shelfmark used by A-Ed. The column “parts” (originally “Partes” and “Stück”) denotes the number of parts that existed when the inventory was assembled.

```{r eisenstadt}
#| echo: false

links <- 
  read_rds("data_generated/works.rds") %>% 
  left_join(
    read_csv("data/catalogue_overview.csv") %>% distinct(group, file),
    by = "group"
  ) %>% 
  unite(group:number, col = "id", sep = ".", na.rm = TRUE) %>%
  unnest(sources, names_sep = "_") %>% 
  separate_wider_delim(
    sources_source,
    delim = " ",
    names = c("siglum", "shelfmark"),
    too_many = "merge"
  ) %>%
  filter(siglum %in% c("A-Ed", "A-El")) %>% 
  select(id, shelfmark, file) %>%
  mutate(
    link = str_glue('<a href="/groups/{file}.html#work-{id}">{id}</a>')
  ) %>% 
  select(!c(file, id))

read_csv("data/inventory_eisenstadt.csv") %>% 
  fill(group, page) %>% 
  separate_longer_delim(shelfmark, delim = ", ") %>% 
  left_join(links, by = "shelfmark") %>%
  summarise(
    .by = c(group, page, number),
    title = first(title),
    parts = first(parts),
    notes = first(notes),
    link = str_flatten_comma(link)
  ) %>% 
  gt(groupname_col = "group") %>%
  cols_align("right", columns = c(page, number, parts)) %>%
  cols_label(page = "p.", number = "no.", link = "WerW") %>% 
  fmt_markdown(columns = link) %>%
  sub_missing(columns = notes, missing_text = "") %>%
  tab_options(
    column_labels.font.weight = "bold",
    row_group.background.color = "grey90",
    table_body.hlines.style = "none"
  )
```



## Fonds Moder

[Richard Moder](https://data.onb.ac.at/nlv_lex/perslex/M/Moder_Richard.html) (1901–1991) studied Gregor Joseph Werner's music intensively and published some of his works for the first time. His Nachlass concerning Werner is available in the Austrian National Library and includes around 190 inventory items. (Another partial Nachlass is archived by the University of Salzburg; however, it does not contain any items related to Werner.) For each item, the following table lists

- its inventory number, linked to the library's catalogue entry
- the folder (some items are collected in a common folder)
- the title
- the catalogue of works number

Items in gray text have not yet been screened.



```{r fonds moder}
#| echo: false

# read contents of the fonds Moder
fonds_data <- 
  read_csv("data/fonds_moder.csv") %>% 
  rename(WerW = id)

# check that entries in the fonds Moder have correct WerW numbers
fonds_cited <- 
  read_rds("data_generated/works.rds") %>% 
  unnest(sources, names_sep = "_") %>%
  filter(str_starts(sources_source, "A-Wn F100")) %>%
  unite(group:number, col = "WerW", sep = ".", na.rm = TRUE) %>%
  select(number = sources_source, WerW) %>%
  mutate(number = str_replace(number, "A-Wn F100.Moder.", ""))

wrong_sources <- 
  fonds_data %>% 
  filter(!is.na(WerW)) %>%
  anti_join(fonds_cited, by = join_by(number, WerW)) %>% 
  filter(check_link)

if (nrow(wrong_sources) > 0) {
  error("wrong WerW number in Fonds Moder ",
        "{str_flatten_comma(wrong_sources$number)}",
        strict = TRUE)
}

# define links to the works
work_links <- 
  read_rds("data_generated/works.rds") %>% 
  left_join(
    read_csv("data/catalogue_overview.csv") %>% distinct(group, file),
    by = "group"
  ) %>% 
  unite(group:number, col = "WerW", sep = ".", na.rm = TRUE) %>%
  mutate(
    link = str_glue('<a href="/groups/{file}.html#work-{WerW}">{WerW}</a>')
  ) %>%
  select(WerW, link) %>% 
  add_row(WerW = "–", link = "–")

# create the table output
fonds_data %>% 
  left_join(work_links, by = "WerW") %>% 
  mutate(
    number =
      if_else(
        is.na(onb),
        number,
        str_glue('<a href="https://data.onb.ac.at/rec/{onb}">{number}</a>')
      ) %>%
      map(html),
    WerW = 
      link %>% 
      replace_na("") %>% 
      map(html)
  ) %>%
  select(number, folder, title, WerW, notes) %>% 
  gt() %>%
  cols_align("left") %>%
  fmt_markdown(columns = notes) %>%
  sub_missing(columns = c(folder, notes), missing_text = "") %>%
  tab_style(
    style = cell_text(color = "grey70"),
    locations = cells_body(rows = is.na(folder))
  ) %>%
  tab_options(
    column_labels.font.weight = "bold",
    table_body.hlines.style = "none"
  )
```


## Hárich's thematic catalogue

The following table reproduces the table of contents of the unfinished catalogue of Werner's works by @Harich1990. Here, we refer to entries in this catalogue by work groups and the (probably final) work numbers, which appear in broad red ink in the top left corner of each card.

```{r harich catalogue}
#| echo: false
#| output: asis

read_csv("data/harich_catalogue.csv") %>% 
  fill(super_number, super_title) %>% 
  unite(super_number, super_title, col = "super", sep = ". ") %>% 
  gt(groupname_col = "super") %>%
  cols_label(number = "", sub = "") %>% 
  sub_missing(missing_text = "") %>%
  tab_style(
    style = list(
      cell_text(weight = "bold"),
      cell_borders("top", color = "#d3d3d3", weight = "2px")
    ),
    locations = cells_body(rows = 34)
  ) %>%
  tab_options(
    column_labels.font.weight = "bold",
    row_group.background.color = "grey90",
    table_body.hlines.style = "none"
  )
```
