---
output: html_document
editor_options: 
  chunk_output_type: console
format:
  html:
    html-table-processing: none
---

# Inventories {.unnumbered}

```{r packages and functions}
#| include: false
library(tidyverse)
library(gt)
source("script/utils.R")
options(readr.show_col_types = FALSE)

print_concordance_ref <- function(ref, patterns) {
  patterns <- c(
    ".+\\[",
    patterns,
    "]"
  )

  read_rds("data_generated/works.rds") %>%
    left_join(
      read_csv("data/catalogue_overview.csv") %>% distinct(group, file),
      by = "group"
    ) %>%
    unite(group:number, col = "id", sep = ".", na.rm = TRUE) %>%
    mutate(id = str_glue("[{id}](/groups/{file}.html#work-{id})")) %>%
    separate_longer_delim(inventories, ", @") %>%
    filter(str_detect(inventories, ref)) %>%
    select(inventories, id) %>%
    separate_wider_regex(
      inventories,
      patterns = {{patterns}}
    ) %>%
    mutate(across(!id, parse_guess)) %>%
    arrange(pick(!id)) %>%
    gt() %>%
    fmt_markdown(columns = id) %>%
    cols_label(id = "WerW") %>% 
    tab_options(
      column_labels.font.weight = "bold",
      table.align = "left",
      table_body.hlines.style = "none"
    )
}
```



## Historic

### @BrtniceInv

```{r Brtnice}
#| echo: false
#| output: asis
print_concordance_ref(
  "BrtniceInv",
  patterns = c(
    "p. ",
    p. = "\\d+",
    ", no. ",
    no. = "\\d+"
  )
)
```


### @EisenstadtInv1837

The inventory of Eisenstadt was finalized in 1837. The table of sources is written on the verso pages, which are numbered (with odd numbers!). For selected entries, the recto pages contain annotations indicating new parts that should be created (column “notes” in the table below). Groups have been numbered with uppercase letters. Thereby, the combination of group letter and inventory number corresponds to the modern shelfmark used by A-Ed. The column “parts” (originally “Partes” and “Stück”) denotes the number of parts that existed when the inventory was assembled.

```{r Eisenstadt}
#| echo: false

links <- 
  read_rds("data_generated/works.rds") %>% 
  left_join(
    read_csv("data/catalogue_overview.csv") %>% distinct(group, file),
    by = "group"
  ) %>% 
  unite(group:number, col = "id", sep = ".", na.rm = TRUE) %>%
  unnest(sources, names_sep = "_") %>% 
  separate_wider_delim(
    sources_source,
    delim = " ",
    names = c("siglum", "shelfmark"),
    too_many = "merge"
  ) %>%
  filter(siglum %in% c("A-Ed", "A-El")) %>% 
  select(id, shelfmark, file) %>%
  mutate(
    link = str_glue('<a href="/groups/{file}.html#work-{id}">{id}</a>')
  ) %>% 
  select(!c(file, id))

read_csv("data/inventory_eisenstadt.csv") %>% 
  fill(group, page) %>% 
  separate_longer_delim(shelfmark, delim = ", ") %>% 
  left_join(links, by = "shelfmark") %>%
  summarise(
    .by = c(group, page, number),
    title = first(title),
    parts = first(parts),
    notes = first(notes),
    link = str_flatten_comma(link)
  ) %>% 
  gt(groupname_col = "group") %>%
  cols_align("right", columns = c(page, number, parts)) %>%
  cols_label(page = "p.", number = "no.", link = "WerW") %>% 
  fmt_markdown(columns = link) %>%
  sub_missing(columns = notes, missing_text = "") %>%
  tab_options(
    column_labels.font.weight = "bold",
    row_group.background.color = "grey90",
    table_body.hlines.style = "none"
  )
```


### @EsterhazyInv1805

```{r Esterhazy 1805}
#| echo: false
#| output: asis
print_concordance_ref(
  "EsterhazyInv1805",
  patterns = c(
    "fol. ",
    fol. = ".+",
    ", no. ",
    no. = "\\d+"
  )
)
```


### @EsterhazyInv1812

```{r Esterhazy 1812}
#| echo: false
#| output: asis
print_concordance_ref(
  "EsterhazyInv1812",
  patterns = c(
    genre = ".+",
    " no. ",
    no. = "\\d+"
  )
)
```


### @Sauer1809

```{r Sauer}
#| echo: false
#| output: asis
print_concordance_ref(
  "Sauer1809",
  patterns = c(
    "fol. ",
    fol. = ".+",
    ", no. ",
    no. = ".+"
  )
)
```



## Modern

### @Bardos1976

```{r Bardos 1976}
#| echo: false
#| output: asis
print_concordance_ref(
  "Bardos1976",
  patterns = c(
    "p. ",
    p. = ".+",
    ", no. ",
    no. = "\\d+"
  )
)
```


### @Bardos1980

```{r Bardos 1980}
#| echo: false
#| output: asis
print_concordance_ref(
  "Bardos1980",
  patterns = c(
    "p. ",
    p. = ".+",
    ", no. ",
    no. = ".+"
  )
)
```


### @Bardos1984

```{r Bardos 1984}
#| echo: false
#| output: asis
print_concordance_ref(
  "Bardos1984",
  patterns = c(
    "p. ",
    p. = ".+",
    ", no. ",
    no. = ".+"
  )
)
```


### @Riedel1979

```{r Riedel}
#| echo: false
#| output: asis
print_concordance_ref(
  "Riedel1979",
  patterns = c(
    "p. ",
    p. = ".+",
    ", no. ",
    no. = ".+"
  )
)
```


### @Rostetter2023

```{r Rostetter}
#| echo: false
#| output: asis
print_concordance_ref(
  "Rostetter2023",
  patterns = c(
    "p. ",
    p. = ".+",
    ", no. ",
    no. = ".+"
  )
)
```


### @Stefan1985

```{r Stefan}
#| echo: false
#| output: asis
print_concordance_ref(
  "Stefan1985",
  patterns = c(
    "p. ",
    p. = ".+",
    ", no. ",
    no. = ".+"
  )
)
```


### Fonds Moder

[Richard Moder](https://data.onb.ac.at/nlv_lex/perslex/M/Moder_Richard.html) (1901–1991) studied Gregor Joseph Werner's music intensively and published some of his works for the first time. His Nachlass concerning Werner is available in the Austrian National Library and includes around 190 inventory items. (Another partial Nachlass is archived by the University of Salzburg; however, it does not contain any items related to Werner.) For each item, the following table lists

- its inventory number, linked to the library's catalogue entry
- the folder (some items are collected in a common folder)
- the title
- the catalogue of works number

Items in gray text have not yet been screened.



```{r fonds moder}
#| echo: false

# read contents of the fonds Moder
fonds_data <- 
  read_csv("data/fonds_moder.csv") %>% 
  rename(WerW = id)

# check that entries in the fonds Moder have correct WerW numbers
fonds_cited <- 
  read_rds("data_generated/works.rds") %>% 
  unnest(sources, names_sep = "_") %>%
  filter(str_starts(sources_source, "A-Wn F100")) %>%
  unite(group:number, col = "WerW", sep = ".", na.rm = TRUE) %>%
  select(number = sources_source, WerW) %>%
  mutate(number = str_replace(number, "A-Wn F100.Moder.", ""))

wrong_sources <- 
  fonds_data %>% 
  filter(!is.na(WerW)) %>%
  anti_join(fonds_cited, by = join_by(number, WerW)) %>% 
  filter(check_link)

if (nrow(wrong_sources) > 0) {
  error("wrong WerW number in Fonds Moder ",
        "{str_flatten_comma(wrong_sources$number)}",
        strict = TRUE)
}

# define links to the works
work_links <- 
  read_rds("data_generated/works.rds") %>% 
  left_join(
    read_csv("data/catalogue_overview.csv") %>% distinct(group, file),
    by = "group"
  ) %>% 
  unite(group:number, col = "WerW", sep = ".", na.rm = TRUE) %>%
  mutate(
    link = str_glue('<a href="/groups/{file}.html#work-{WerW}">{WerW}</a>')
  ) %>%
  select(WerW, link) %>% 
  add_row(WerW = "–", link = "–")

# create the table output
fonds_data %>% 
  left_join(work_links, by = "WerW") %>% 
  mutate(
    number =
      if_else(
        is.na(onb),
        number,
        str_glue('<a href="https://data.onb.ac.at/rec/{onb}">{number}</a>')
      ) %>%
      map(html),
    WerW = 
      link %>% 
      replace_na("") %>% 
      map(html)
  ) %>%
  select(number, folder, title, WerW, notes) %>% 
  gt() %>%
  cols_align("left") %>%
  fmt_markdown(columns = notes) %>%
  sub_missing(columns = c(folder, notes), missing_text = "") %>%
  tab_style(
    style = cell_text(color = "grey70"),
    locations = cells_body(rows = is.na(folder))
  ) %>%
  tab_options(
    column_labels.font.weight = "bold",
    table_body.hlines.style = "none"
  )
```
