---
output: html_document
editor_options: 
  chunk_output_type: console
format:
  html:
    html-table-processing: none
---

# Inventories {.unnumbered}

```{r}
#| include: false
library(tidyverse)
library(gt)
source("script/utils.R")
options(readr.show_col_types = FALSE)
```

## Fonds Moder

[Richard Moder](https://data.onb.ac.at/nlv_lex/perslex/M/Moder_Richard.html) (1901–1991) studied Gregor Joseph Werner's music intensively and published some of his works for the first time. His Nachlass is available in the Austrian National Library and includes around 190 inventory items. For each item, the following table lists

- its inventory number, linked to the library's catalogue entry
- the folder (some items are collected in a common folder)
- the title
- the catalogue of works number

Items in gray text have not yet been screened.

```{r}
#| echo: false
#| output: asis

# read contents of the fonds Moder
fonds_data <- 
  read_csv("data/fonds_moder.csv") %>% 
  rename(WerW = id)

# check that entries in the fonds Moder have correct WerW numbers
fonds_cited <- 
  read_rds("data_generated/works.rds") %>% 
  unnest(sources, names_sep = "_") %>%
  filter(str_starts(sources_source, "A-Wn F100")) %>%
  left_join(
    read_csv("data/catalogue_overview.csv") %>% distinct(group, file),
    by = "group"
  ) %>% 
  unite(group:number, col = "WerW", sep = ".", na.rm = TRUE) %>%
  select(number = sources_source, WerW, file) %>%
  mutate(number = str_replace(number, "A-Wn F100.Moder.", ""))

wrong_sources <- 
  fonds_data %>% 
  filter(!is.na(WerW)) %>%
  anti_join(fonds_cited, by = join_by(number, WerW))

if (nrow(wrong_sources) > 0)
  error("wrong WerW number in Fonds Moder ",
        "{str_flatten_comma(wrong_sources$number)}")

# create the table output
fonds_data %>% 
  left_join(fonds_cited, by = join_by(number, WerW)) %>% 
  mutate(
    number =
      if_else(
        is.na(onb),
        number,
        str_glue('<a href="https://data.onb.ac.at/rec/{onb}">{number}</a>')
      ) %>%
      map(html),
    WerW = 
      if_else(
        is.na(WerW),
        "",
        str_glue("[{WerW}](/groups/{file}.html#work-{WerW})")
      )
  ) %>% 
  select(number, folder, title, WerW, notes) %>% 
  gt() %>% 
  cols_align("left") %>% 
  fmt_markdown(columns = WerW) %>% 
  sub_missing(missing_text = "") %>% 
  tab_style(
    style = cell_text(color = "grey70"),
    locations = cells_body(rows = is.na(folder))
  ) %>% 
  tab_options(
    column_labels.font.weight = "bold",
    table_body.hlines.style = "none"
  ) %>%
  {.} 
```
