---
output: html_document
editor_options: 
  chunk_output_type: console
format:
  html:
    html-table-processing: none
---

# Inventories {.unnumbered}

```{r packages}
#| include: false
library(tidyverse)
library(gt)
source("script/utils.R")
options(readr.show_col_types = FALSE)
```

## Fonds Moder

[Richard Moder](https://data.onb.ac.at/nlv_lex/perslex/M/Moder_Richard.html) (1901–1991) studied Gregor Joseph Werner's music intensively and published some of his works for the first time. His Nachlass concerning Werner is available in the Austrian National Library and includes around 190 inventory items. (Another partial Nachlass is archived by the University of Salzburg; however, it does not contain any items related to Werner.) For each item, the following table lists

- its inventory number, linked to the library's catalogue entry
- the folder (some items are collected in a common folder)
- the title
- the catalogue of works number

Items in gray text have not yet been screened.



```{r fonds moder}
#| echo: false

# read contents of the fonds Moder
fonds_data <- 
  read_csv("data/fonds_moder.csv") %>% 
  rename(WerW = id)

# check that entries in the fonds Moder have correct WerW numbers
fonds_cited <- 
  read_rds("data_generated/works.rds") %>% 
  unnest(sources, names_sep = "_") %>%
  filter(str_starts(sources_source, "A-Wn F100")) %>%
  unite(group:number, col = "WerW", sep = ".", na.rm = TRUE) %>%
  select(number = sources_source, WerW) %>%
  mutate(number = str_replace(number, "A-Wn F100.Moder.", ""))

wrong_sources <- 
  fonds_data %>% 
  filter(!is.na(WerW)) %>%
  anti_join(fonds_cited, by = join_by(number, WerW)) %>% 
  filter(check_link)

if (nrow(wrong_sources) > 0) {
  error("wrong WerW number in Fonds Moder ",
        "{str_flatten_comma(wrong_sources$number)}",
        strict = TRUE)
}

# define links to the works
work_links <- 
  read_rds("data_generated/works.rds") %>% 
  left_join(
    read_csv("data/catalogue_overview.csv") %>% distinct(group, file),
    by = "group"
  ) %>% 
  unite(group:number, col = "WerW", sep = ".", na.rm = TRUE) %>%
  mutate(
    link = str_glue('<a href="/groups/{file}.html#work-{WerW}">{WerW}</a>')
  ) %>%
  select(WerW, link) %>% 
  add_row(WerW = "–", link = "–")

# create the table output
fonds_data %>% 
  left_join(work_links, by = "WerW") %>% 
  mutate(
    number =
      if_else(
        is.na(onb),
        number,
        str_glue('<a href="https://data.onb.ac.at/rec/{onb}">{number}</a>')
      ) %>%
      map(html),
    WerW = 
      link %>% 
      replace_na("") %>% 
      map(html)
  ) %>%
  select(number, folder, title, WerW, notes) %>% 
  gt() %>%
  cols_align("left") %>%
  fmt_markdown(columns = notes) %>%
  sub_missing(columns = c(folder, notes), missing_text = "") %>%
  tab_style(
    style = cell_text(color = "grey70"),
    locations = cells_body(rows = is.na(folder))
  ) %>%
  tab_options(
    column_labels.font.weight = "bold",
    table_body.hlines.style = "none"
  )
```


## Hárich's thematic catalogue

The following table reproduces the table of contents of the unfinished catalogue of Werner's works by @Harich1990. Here, we refer to entries in this catalogue by work groups and the (probably final) work numbers, which appear in broad red ink in the top left corner of each card.

```{r harich catalogue}
#| echo: false
#| output: asis

read_csv("data/harich_catalogue.csv") %>% 
  fill(super_number, super_title) %>% 
  unite(super_number, super_title, col = "super", sep = ". ") %>% 
  gt(groupname_col = "super") %>%
  cols_label(number = "", sub = "") %>% 
  sub_missing(missing_text = "") %>%
  tab_style(
    style = list(
      cell_text(weight = "bold"),
      cell_borders("top", color = "#d3d3d3", weight = "2px")
    ),
    locations = cells_body(rows = 34)
  ) %>%
  tab_options(
    column_labels.font.weight = "bold",
    row_group.background.color = "grey90",
    table_body.hlines.style = "none"
  )
```
